\section{Talagrand's convex concentration theorem}


Let $\Omega = \OxN$. Recall the Hamming distance of $X,Y\in \Omega$ given by $d_H(X,Y)= \sumn \ONE[X_n \neq Y_n]$. In the following, we work with a generalized Hamming distance defined in terms of $a \in S^{N-1}\cap \RR_+^N=: S_+^N$: 
$$d^{(a)}H(X,Y)=\sumn a_n\ONE[X_n \neq Y_n]$$


\begin{remark}
  For any \(A\ssq \Omega, \; f_A: \Omega \to [0,\infty)\) with 
  \[f_A(x)=d_H^{a}(x,A)=\min_{y\in A}d_H^{a}(x,y)\] 
  satisfies the BD condition, i.e.
  \[f_A( X_1 , \dots, X_{n-1} ),X_n, X_{n+1} , \dots , X_N ) - f_A( X_1 , \dots , X_{n+1}, X_n', X_{n+1} , \dots , X_N  ) \leq a_n \]
  We can apply Azuma's inequality for all \( \lambda>0\) and obtain 
  \[ \mathbb{P}(\abs{f})\]
\end{remark}


\begin{defn}[Talagrand distance]
    For \(A\ssq \Omega\) we set the Talagrand distance 
    \[d_T(x,A):= \sup_{a\in S_+^N} d_H^{(a)}(x,A)\]
    with \(S_+^N := S^{N-1 \cap \RR^N_+}\)
\end{defn}


\begin{lem}[]
  Let \(A\ssq [0,1]^N\) be convex. Then, for any \( x\in [0,1]^N\), we have 
  \[d_2(x,A) \leq d_T(x,A)\]
\end{lem}


\begin{thm}[Talagrand]
    Let \(X= ( X_1 , \dots , X_N ) \in \Omega\) be independent random variables and \(A \ssq \Omega\) measurable. Then, there is some \(c>0\) and for any \( \lambda\):
    \[\min \cub{\PP, \PP(A_{ \lambda^c}}\leq \exp(-c \lambda^2)\]
    where \(A_\lambda:= \cub{y \in \Omega \fil d_T(y,A) \leq \lambda}\).
\end{thm}


\begin{defn}[Quasi-convvexity]
  Let \(U\in \RR^N\) be convex. A function \(f:U \to \RR\) is called quasi-convex if for all \(u\in \RR\) the set \(\cub{x \in U \fil f(x) \leq u}\) is convex.
\end{defn}


\begin{defn}[Talagrand concentration for quasi-convex functions]
  Let \(f:[0,1]^N \to \RR\) be a 1-Lipschitz and quasi-convex function. Let \( (X_1 , \dots , (X_N) \in [0,1]^N  \) be independent random variables. Then, there is $c>0$ such that for all \( \lambda>0\)
  \[\PP(\abs{f(X)-Mf(X)> \lambda}) \leq 2 \exp(-c \lambda^2)\]
\end{defn}


\begin{corl}[]
  Let \(A \in \RR^{N \times N}\) be random with independent entries such that \( \abs{A_{n,m}} \leq 1\) almost surely. Then, there is $c>0$ such that for all \( \lambda>0\)
  \[\PP(\abs{ \norm{A}- M\norm{A} }> \lambda) \leq 2 \exp(-c \lambda^2)\]
\end{corl}


\begin{corl}[Alon-Krivelevich-Vu]
  Let \(A=A^t \in \RR^{N \times N}\) be a hermitian random matrix with independent entries such that  \(\abs{A_{n,m}}\leq 1\). Let \( \lambda(A)_1 \leq \dots \leq \lambda(A)_N \) be their ordered eigenvalues. Then, for all \(n\in \cub{ 1,\dots,N} \) and all \( \lambda>0\)
  \[\PP(\abs{\lambda_n(A)-M\lambda_n(A)}> \lambda ) \leq 2 \exp \left(- \\frac{c \lambda^2}{n^2}\right)\]
\end{corl}

  
